\documentclass{myresume2}
\begin{document}
%
\theHeader
  {Yan Jie, Kee}
  {\href{mailto:keeyanjie2013@gmail.com}{\underline{keeyanjie2013@gmail.com}}}
  {+44 7407 316805}
%
%
%
%
\section{Summary}
\paragraphEntry{A hardworking and motivated individual, I was awarded the Zepler Prize for having the top mark in Electrical \& Electronic Engineering Part I, 2018/19. I am proficient in System Verilog, C, C++ programming languages as well as a number of simulation software programmes. While I am keen on maths, I also have the tendency to be especially persistent when it comes to solving problems. It is my philosophy to truly understand the underlying principle of something that piques my interest.}%
%
%
%
\section{Education}
%
\headEntry
  {University of Southampton}
  {2018-}
  {MEng in Electronic Engineering, Third Year}
  {2022}
\twocolumnEntry
  {Modules:}
  {\begin{tabular*}{\linewidth}{@{}p{2.3cm}p{\linewidth-2.3cm}@{}}
    \textit{First Year:} & Digital System \& Microprocessor\s Advanced Programming\s Electronic System\s Mathematics for EEE\s \textit{(Overall mark: 90\%)}\vspace{1ex}\\
    \textit{Second Year:} & Digital System \& System Processing\s Computer Engineering\s Electronic Design\s Control \& Communication\s Advanced Electronic Systems\\
    \end{tabular*}
  }\vspace{1.5ex}

  % First Year : Digital System \& Microprocessor\bigs Advanced Programming\bigs Electronic System\newline
  % Second Year : Digital System \& System Processing\bigs Computer Eningeering\bigs Electronic Design\bigs Control \& Communication

\twocolumnEntry
  {Projects:}
  {%
  \projectEntry
    {Digital Stopwatch Design}
    {Oct 2019}
    {\item A stopwatch with 99.9 seconds range consisting of synchronous counters, a nibble multiplexer and a seven-segment decoder
    \item Designs are simulated on an IC design environment and sent for fabrication
    \item Circuits are fitted on an area of 146$\mu$m x 135$\mu$m, part of TSMC 0.18$\mu$m-tech chip}
    {Software: Tanner S-edit, L-Edit}

  \projectEntry
    {Interactive Whiteboard Client-server}
    {May 2019}
    {\item An interactive whiteboard which pairs of users can use to view and edit on their respective Raspberry Pi simultaneously
    \item Created a GUI for better user experience using a widget toolkit, Qt5
    \item Designed a communication protocol that is connected by the Raspberry Pis' GPIO
    \item Implemented a thread-safe environment with pThread library}
    {Languages: C++}

  \projectEntry
    {Digital System and Microprocessor Design}
    {Jan 2019}
    {\item Design a simple microprocessor using System Verilog and run it on the DE1-SoC Development Board (Altera Cyclone V FPGA)
    \item Microprocessor modules functionalities are verified in a simulation environment
    \item Instruction sets are modified to perform XOR-cipher encryption and decryption tasks.}
    {Languages: System Verilog\bigs Software: ModelSim, Quartus}
  }

\headEntry
  {UEM Foundation College, KYUEM}
  {2017-}
  {Cambridge A-Level}
  {2018}
\twocolumnEntry
  {Grades:}
  {Physics (A*), Chemistry (A*), Mathematics (A*), Further Mathematics (A*)}
\twocolumnEntry
  {Prizes:}
  {Certificate of Acheivement: Excellence in the subject of Further Mathematics for Semester of July to December 2017}
\pagebreak
%
%
%
%
\section{Achievements}
\simpleEntry
  {Zepler Prize 2018/19}
  {Nov 2019}
  {\item Top mark in Electrical \& Electronic Engineering Part I 2018/19 with a grade average of 90\%}

\simpleEntry
  {Master of Mainframe Part 2 Badge}
  {Dec 2019}
  {\item Completed Part 2 of the challenge about the latest IBM-Z mainframe.
  \item Gained experience with programming languages like Db2, JCL and operating system z/OS.}
%
%
%
%
\section{Technical Skills}
\twocolumnEntry
  {Coding\newline Languages:}
  {C, C++, System Verilog, MATLAB}
\twocolumnEntry
  {Software:}
  {ModelSim, Quartus, LT-Spice, Tanner S-edit, L-edit, EAGLE PCB Software}
\twocolumnEntry
  {Other:}
  {Git, Embedded system, Qt5, LaTeX}
%
%
%
%
\section{Extracurricular Activities}
%
\simpleEntry
  {Malaysian Students Association - Male Sports Officer}
  {May 2018 - present}
  {\item Taking care of the welfare of Malaysian students studying at the University.
  \item Arrange weekly sports session and occasional sports events for the society members.}

\simpleEntry
  {Nepal Project (Student-led) – Event manager}
  {Jun 2017}
  {\item Responsible for the cultural trip planning and directing performances for visitation to schools, orphanage and monastery at Nepal
  \item Fundraised primarily for schools severely affected by the 2008 earthquake}

\simpleEntry
  {Cross-country Running – President}
  {Jun 2015}
  {\item Assign tasks to sub-groups and have regular meetings to ensure cooperation between team leaders.
  \item Manage event involving 1000+ participants and ensure the safety of every student}
%
%
%
%
\section{Interests}
%
\twocolumnEntry
  {Basketball}
  {A passion that has been following me for more than 10 years. I played competitively during high school}
\twocolumnEntry
  {Reading}
  {Particularly inclined towards Popular Science genre, for example, \textit{Thinking Fast and Slow} by Daniel Kahneman.}
%
\section{Languages}
\textit{English (Fluent)\bigs Mandarin (Native)\bigs Malay (Native)}
%
\section{References}
\paragraphEntry{Dr Jize Yan (Personal Tutor, University of Southampton) \href{mailto:j.yan@southampton.ac.uk}{\underline{j.yan@southampton.ac.uk}}}
%
\end{document}
